Computational hysteresis:\\ inter-task effects in human computation

### 2014-10-12 docs/publications/2014.09_SCIENCE/ban.tex
work on manuscript

\title{Human computational hysteresis: measuring inter-task effects}

@@

\author
{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
\\
\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

@@

Such repetition effects, or
\textit{inter-task effects}, are neither random, nor are they formally part 
of the instructions given to the HPU.  The ``leakage'' of information from 
recently performed tasks into HPU outputs is a potentially strong source of 
systematic bias, which complicates the the algorithmic view of HPUs. 
Inter-task effects would amount to a kind of \textit{hysteresis}, meaning 
that HPU output is not only a function of the current input, but also of the 
history of inputs.

Here we make two contributions towards understanding inter-task effects
and HPU hysteresis in general.  We present a framework for treating this 
source of bias in the context of HPU algorithms, and we measure the impact of
inter-task effects experimentally in a canonical HPU task: the labeling of 
images.

Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
perform a series of image-labeling tasks.  
In these tasks, workers labeled images featuring iconic cultural scenes,
food, table-settings, and various utensils and cookware. We divided the set of 
images shown to a given worker into an \textit{initial} and \textit{test} set, 
but, crucially, there was no apparent distinction between these sets from the
perspective of the worker.  We varied the initial set of images, while 
keeping the test set the same, to analyze the effect that that the initial 
images had on the labels that workers attributed to the test set.

@@

As a point of comparison, we included treatments in which we induce 
\textit{framing}.
Before the workers label images, we indicate that the work 
was funded by a research lab having a particular area of interest, to see the 
influence this has on the workers’ subsequent labels. 
Surprisingly, inter-task effects were stronger than framing, in some cases 
about twice as strong. 
Our results show that initial tasks can significantly alter the subject 
matter on which worker's labels focus. We also found that inter-task 
effects can induce workers to provide labels of greater or lesser specificity. 
This suggests that careful consideration should be given to the bundling of 
tasks when designing a study using a microtask platform.

To characterize inter-task effects, we present a novel, generalized definition 
of \textit{HPU priming}. Priming is traditionally used to elucidate the
internal psychological mechanisms of cognition.  But here we are concerned with
understanding the outward effects that priming phenomena have on HPU 
algorithms. Thus, before we discuss inter-task effects experimentally, we 
discuss formal definitions for priming as computational phenomenon.  Our
discussion will lead to a natural definition of priming that enables 
comparisons of the severity priming effects accross applications, and enables
the measurement of priming using machine learning tools.

\paragraph*{Priming as computational hysteresis.}
To begin, we adopt the perspective that there is no canonical neutral or
unprimed state.  Rather, we will speak of one HPU population being 
\textit{differently primed} from another.  We present three definitions for 
the difference in priming between HPU populations, each having different 
merits, and then we discuss their relationships. To proceed with the 
definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ and 
$\mathcal{Q}$ were 
sampled randomly from the same initial population $\mathcal{R}$, and then were 
exposed to (possibly) different priming treatments. The HPUs in $\mathcal{P}$ 
and $\mathcal{Q}$ perform some task, leading to popualtions of work-products, 
$P$ and $Q$.

For the first defenition, we focus on the direct effects that running an 
algorithm on differently primed HPUs has on the algorithm's output.

\begin{mydef}
	\label{def:bias}
	{\upshape Maximum Bias $\theta_\mathrm{bias}$:}
	Let $\mathcal{D}$ be a binary decision algorithm, which takes a 
	work-product
	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
	$\theta^\mathcal{D}_\mathrm{bias}(P,Q)$ and define it to be the difference 
	in the expected output of $\mathcal{D}$ when acting on work-products from 
	$P$ and $Q$:
	$$
	\theta^\mathcal{D}_\mathrm{bias}(P,Q) = 
		\left| 
			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
		\right|,
	$$
	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
	the bias of the most susceptible decision:
	$$
	\theta_\mathrm{bias} = 
		\sup_\mathcal{D} \theta^\mathcal{D}_\mathrm{bias}(P,Q)
	$$
\end{mydef}
Thus, in \textbf{Definition \ref{def:bias}}, $\theta_\mathrm{bias}$ has a 
straightforward interpretation as an upper bound on the amount of bias induced 
on any yes-or-no decision, due to the difference in priming of 
$\mathcal{P}$ and $\mathcal{Q}$.  Although easy to interpret, it is, however, 
not clear how $\theta_\mathbf{bias}$ could be measured in practice.

Next we attempt to phase the difference in priming between $\mathcal{P}$ and
$\mathcal{Q}$ in terms of the extent to which their work products are 
distinguishable algorithmically. To facilitate this definition, we make 
use of the notions of a \textit{distinguisher} and a \textit{validation} test.
\begin{mydef}
	{\upshape Algorithmic distinctness $\theta_\mathrm{dist}$:}
	Let $\mathcal{D}$ be a distinguisher algorithm, which takes work-product 
	$r \in P \cup Q$ as input, and outputs a \emph{guess} 
	$\mathcal{D}(r) \in \{0, 1\}$. Now define a validation test 
	$V(\mathcal{D}, R_0, R_1)$ as follows. A bit is drawn uniformly at random, 
	$b \in_R \{0, 1\}$, and then a work-product $r$ is chosen uniformly at 
	random from one of the populations, decided by the bit: $r \in_R R_b$. 
	Feed $r$ to $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
	$\mathcal{D}$ guessed correctly, and the value of $V$ is 1, 
	otherwise $V = 0$.

	A distinguisher that guesses randomly will still be correct half of the 
	time. Therefore, denote the performance of $\mathcal{D}$ as 
	$\eta_\mathcal{D}(P, Q)$:
	$$
		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1
	$$
	Then define the difference in priming between $\mathcal{P}$ and 
	$\mathcal{Q}$ to be the performance of the best possible distinguisher:
	$$ 
		\theta_\mathrm{dist} = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
	$$
\end{mydef}
In the above definition, the performance simply rescales accuracy, so that when
accuracy is 1/2 (i.e. as good as chance) performance is 0, and when accuracy 
is perfect, performance is 1. This definition formulates the measurement of 
priming effects in terms of a binary classification problem. As we will show,
this allows us to apply tools from the machine learning field to the 
measurement of difference in priming.  However, it is not immediately clear 
how this measure relates to the potential for priming to cause bias.

For the third definition, we focus on describing the inherent, statistical
difference between work-products in $P$ and $Q$. Thus we define the difference
in priming to be equal to the \textit{total variational distance}, or $l_1$-distance (denoted $D_{l_1}$) between $P$ and $Q$. 
\begin{mydef}
	\label{def:l1}
	{\upshape total variational distance $\theta_{l_1}$:}
	$$
	\theta_{l_1} = D_{l_1}(P,Q) \equiv \frac{1}{2} \sum_{x \in \mathcal{X}} 
	\left| 
		f_P(x) - f_Q(x)
	\right|,
	$$
	where $f_P(x)$ denotes the probability of observing x when sampling from P.
\end{mydef}
The abvantage of definition \ref{def:l1} is that it provides connections
to statistical and information theory.

Remarkably, all three definitions are, in fact, equivalent, and from here on
we simply denote the difference in priming as $\theta$.  We provide proofs
in the supplementary material to demostrate this fact.  This means that we
can use machine learning tools to measure priming, while interpreting the
results either in terms of the  leakage of information from a prime into an 
HPU output or in terms of the potential to bias a decision.

\paragraph{Measuring priming.}
Before proceeding, we offer a few words of caution regarding the measurement 
of $\theta$.

Care must be taken in estimating $D_{l_1}$ from samples so as not to obtain
an inflated estimate. In the so-called naive approach, one uses the frequency 
with which a given work-product $x$ is obtained from HPUs in $\mathcal{P}$ to 
estimate the probability mass function at $x$; 
$\hat{f}_P(x) = (\sum_{X\in P} \mathbf{1}_{[X=x]})/|P|$.
One can then estimate 
$D_{l_1} = \sum_{x \in \mathcal{X}} \left|\hat{f}_P(x) - \hat{f}_Q(x) \right|/2$ using only the sample frequencies. But the number of samples, $|P|$ and 
$|Q|$, must be much larger than the number of possible work-outputs, 
$|\mathcal{X}|$, otherwise, this method produces an enormously inflated 
estimate.

Recently, attempts have been made to provide better estimators. Valiant, 
provides a canonical estimation approach based on first estimating the unseen 
region of the support. This algorithm appears to perform very well in practice.
Batu provided an alternative approach, which bypasses estimating the 
probability mass functions, and relies on the more fundamental concept of 
\textit{collisions}.

Both methods converge much more quickly than the naive approach. However, two 
limitations remain that prevent their application. First, these relatively 
recent approaches are not accompanied by any absolute guarantees of 
statistical confidence, so it is not yet clear how to build confidence 
intervals for a given estimate. Second, sophisticated as these methods are, 
they still cannot provide reliable estimates when none of the elements of the 
support recur in the samples (that is, when we never observe the same 
work-product twice in our sample sets).

It may seem unreasonable to hope to measure $D_{l_1}$ when our samples are so 
megre that no specific work-product recurrs, but this level of sparsity is 
routinely faced in classification tasks. As a concrete example, a facial 
recognition 
system (which classifies images as face or non- face) is expected to work on 
images that have never been seen before, and its design cannot be predicated on
covering a significant fraction of all possible images during training. In our 
experiment, we demonstrate that the quintessential microtask, image labeling, 
is one for which the measurement of priming effects can be approached using 
classifiers.

\paragraph{Experimental setup.}

image labeling is common\ldots
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.

We solicited 2300 MTurk workers to perform an image-labeling task using images 
that depicted meals, place-settings, and related items such as dishes, and 
kitchenware, and other artifacts naturally arising in dining contexts. Workers 
were randomly assigned into one of four treatments, described below. In all 
treatments, workers were given brief instruc- tions before labeling any images.
In some treatments, workers were then also shown a \textit{framing slide}, 
indicating 
the tasks were funded by a group having a particular research focus. The tasks 
consisted of single images, and workers were asked to provide five descriptive 
labels for each. The last five images that workers labeled, the 
\textit{test set}, were the same for all treatments.

The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
\textit{initial set} of five images labeled by workers contained objects such 
as utensils, kitchenware, and table-settings, but no food items. In the 
\textsc{img:food}, the initial set contained centered close-ups of meals, 
without
any surrounding objects (except sometimes the dish supporting the food). No 
interruption or distinction made between the initial and test sets from the 
view of the workers. To study the positional dependance of inter-task effects,
these treatments were subdivided, and workers were shown one of five 
permutations. There are of course 5! = 120 permutations of five images, but 
investigating all permutations was too expensive, and probably redundant, so 
we chose 5 permutations that ensure each image occupies each position within 
the test set. We discuss the benefits and drawbacks of this choice in the 
supplementary material.

Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
framing slide, which bore a message reading: ``Funded by the laboratory for 
the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
After the framing slide, workers in these treatments proceeded directly to 
the test set (and so labeled only 5 images).

\paragraph{The strength of inter-task effects}
We tested for inter-task effects by training a Naive Bayes classifier to 
classify work-products among IMG:OBJ and IMG:FOOD, using only the labels 
attributed to the test set of images. Based on Definition 2, no classifier 
can perform better than the actual difference in priming, so the performance 
of Naive Bayes classifier provides a lower bound on priming difference. We 
used leave-one-out validation to estimate the classifier per- formance. We 
tested for framing effects in a similar way, by training a Naive Bayes 
classifier to classify work-products among \textsc{frm:food} and 
\textsc{frm:obj}.

@@

\paragraph{Inter-task effects and the orientation of focus.}
Since the initial images were chosen to emphasize either food (ingredients 
set) or culture (cultural set), we looked for effects on the number of 
culture- and food-oriented labels that workers attributed to the test image 
set.

>>>>

\title{Computational hysteresis:\\ inter-task effects in human computation}

@@

\author
{Edward Newell, Derek Ruths,\\
\\
\normalsize{\texttt{edward.newell@mail.mcgill.ca}}\\
\normalsize{\texttt{druths@networkdynamics.org}}\\
\normalsize{School of computer science, McGill University,}\\
\normalsize{3630 rue University, Montreal, Quebec, H3A 0C6, Canada}\\
\\
}

@@

Such repetition effects, or
\textit{inter-task effects}, are neither random, nor are they formally part 
of the instructions given to the HPU.  The ``leakage'' of information, 
from recently performed tasks, into HPU outputs, is a potentially strong 
source of systematic bias.
Inter-task effects would amount to a kind of \textit{hysteresis}, meaning 
that HPU output is not only a function of the current input, but also of the 
history of inputs.

Here we make two contributions towards understanding inter-task effects,
and HPU hysteresis in general.  We present a framework for treating this 
source of bias in the context of HPU algorithms, and we measure the impact of
inter-task effects experimentally.

Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
perform a series of image-labeling tasks.  We chose this as the canonical
microtask because image labeling tasks are one of the most common kinds of
microtasks
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
and it seems likely that human computation will have a long-term role
in computer vision research \cite{5543192}.
In these tasks, workers labeled images featuring iconic cultural scenes,
food, table-settings, and various utensils and cookware. We divided the set of 
images shown to a given worker into an \textit{initial} and \textit{test} set, 
but, crucially, there was no apparent distinction between these sets from the
perspective of the worker.  We varied the initial set of images, while 
keeping the test set the same, to analyze the effect that that the initial 
images had on the labels that workers attributed to the test set.

@@

As a point of comparison, we included treatments in which we induce 
\textit{framing}.
Before the workers label images, we indicate that the work 
was funded by a research lab having a particular area of interest, to see the 
influence this has on the workers’ subsequent labels. 
Surprisingly, inter-task effects were stronger than framing, in some cases 
about twice as strong. 
Our results suggest that initial tasks can change what workers choose to focus
in in later tasks.  We also found that inter-task 
effects altered the level of specificity of worker's labels.  This suggests 
that careful consideration should be given to the bundling of 
tasks when designing a study using a microtask platform.

To characterize inter-task effects, we present a novel, generalized definition 
of \textit{HPU priming}. Priming is traditionally used to elucidate the
internal psychological mechanisms of cognition.  But here we are concerned with
understanding the outward effects that priming phenomena have on HPU 
algorithms. Thus, before we discuss inter-task effects experimentally, we 
describe candidate definitions for priming as computational phenomenon.  This 
leads to a natural definition of priming that provides a consistent measure of 
the severity of priming accross applications, and enables the measurement of 
priming using machine learning tools.

\paragraph*{Priming as computational hysteresis.}
To begin, we adopt the perspective that there is no canonical neutral or
unprimed state.  Rather, we will speak of one HPU population being 
\textit{differently primed} from another.  We present three definitions for 
the difference in priming between HPU populations, each with different 
advantages, and then we discuss their relationships. To proceed with the 
definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ and 
$\mathcal{Q}$ were 
sampled randomly from the same initial population $\mathcal{R}$, and then were 
exposed to (possibly) different priming treatments. The HPUs in $\mathcal{P}$ 
and $\mathcal{Q}$ perform some task, leading to popualtions of work-products, 
$P$ and $Q$.

For the first defenition, we focus on the effect that differently primed
HPUs can have on the output of a human computation algorithm.

\begin{mydef}
	\label{def:bias}
	{\upshape Maximum Bias $\theta_\mathrm{bias}$:}
	Let $\mathcal{D}$ be a binary decision algorithm, which takes a 
	work-product
	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
	$\theta^\mathcal{D}_\mathrm{bias}(P,Q)$ and define it to be the difference 
	in the expected output of $\mathcal{D}$ when acting on work-products from 
	$P$ and $Q$:
	$$
	\theta^\mathcal{D}_\mathrm{bias}(P,Q) = 
		\left| 
			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
		\right|,
	$$
	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
	the bias of the most susceptible decision:
	$$
	\theta_\mathrm{bias} = 
		\sup_\mathcal{D} \theta^\mathcal{D}_\mathrm{bias}(P,Q)
	$$
\end{mydef}
In \textbf{Definition \ref{def:bias}}, $\theta_\mathrm{bias}$ has the 
straightforward interpretation as an upper bound on the amount of bias induced 
on any yes-or-no decision, due to the difference in priming of 
$\mathcal{P}$ and $\mathcal{Q}$.  Though easy to interpret, it is admittedly
not clear how $\theta_\mathbf{bias}$ could be measured in practice.

Next we to phrase the difference in priming between $\mathcal{P}$ and
$\mathcal{Q}$ in terms of the extent to which their work-products are 
distinguishable algorithmically. To facilitate this definition, we make 
use of the notions of a \textit{distinguisher} and a \textit{validation test}.
\begin{mydef}
	{\upshape Algorithmic distinctness $\theta_\mathrm{dist}$:}
	Let $\mathcal{D}$ be a distinguisher algorithm, which takes work-product 
	$r \in P \cup Q$ as input, and outputs a \emph{guess} 
	$\mathcal{D}(r) \in \{0, 1\}$. Now define a validation test 
	$V(\mathcal{D}, R_0, R_1)$ as follows. A bit is drawn uniformly at random, 
	$b \in_R \{0, 1\}$, and then a work-product $r$ is chosen uniformly at 
	random from one of the populations, decided by the bit: $r \in_R R_b$. 
	Input $r$ into $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
	$\mathcal{D}$ \emph{guessed correctly}, and the value of $V$ is 1, 
	otherwise $V = 0$.

	A distinguisher that guesses randomly will still be correct half of the 
	time. Therefore, denote the performance of $\mathcal{D}$ by 
	$\eta_\mathcal{D}(P, Q)$, and let
	$$
		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1.
	$$
	Then define the difference in priming between $\mathcal{P}$ and 
	$\mathcal{Q}$ to be the performance of the best possible distinguisher:
	$$ 
		\theta_\mathrm{dist} = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
	$$
	\label{def:dist}
\end{mydef}
In \textbf{definition \ref{def:dist}}, the performance simply rescales 
accuracy, so that when
accuracy is 1/2 (i.e. no better than chance) performance is 0, and when 
accuracy is perfect, performance is 1. This definition formulates the 
measurement of 
priming effects in terms of a binary classification problem. As we will show,
this allows us to apply machine learning tools to the 
measurement of priming.  However, it is not immediately clear 
how this measure relates to the potential for priming to cause bias.

For the third definition, we focus on describing the inherent, statistical
difference between work-products in $P$ and $Q$.  
\begin{mydef}
	\label{def:l1}
	{\upshape Total variational distance $\theta_{l_1}$:}
	Define the difference in priming between $\mathcal{P}$ and $\mathcal{Q}$ 
	to be equal to the total variational distance (also known as 
	$l_1$-distance, denoted $D_{l_1}$) between the work-products $P$ and $Q$:
	$$
	\theta_{l_1} = D_{l_1}(P,Q) \equiv \frac{1}{2} \sum_{x \in \mathcal{X}} 
	\left| 
		f_P(x) - f_Q(x)
	\right|,
	$$
	where $f_P(x)$ denotes the probability of observing x when sampling from P.
\end{mydef}
The advantage of \textbf{definition \ref{def:l1}} is that it provides connections
to statistical and information theory.

Remarkably, all three definitions are, in fact, equivalent, and from here on
we simply denote the difference in priming as $\theta$.  We provide proofs
of this fact in the supplementary material.  This means that we
can use machine learning tools to measure priming, while interpreting the
results either in terms of the  leakage of information from a prime into an 
HPU output or in terms of the potential to bias a decision.

\paragraph{Measuring priming.}
Before proceeding, we offer a few words of caution regarding the measurement 
of $\theta$.  In the so-called naive approach, one uses the frequency 
with which a given work-product $x$ is obtained from HPUs in $\mathcal{P}$ to 
estimate the probability mass function at $x$; 
$\hat{f}_P(x) = (\sum_{X\in P} \mathbf{1}_{[X=x]})/|P|$.
One can then estimate 
$
D_{l_1} = 
	\sum_{x \in \mathcal{X}} \left|\hat{f}_P(x) - \hat{f}_Q(x) \right|/2
$ 
using only the sample frequencies. But the number of samples, $|P|$ and 
$|Q|$, must be much larger than the number of possible work-outputs, 
$|\mathcal{X}|$, otherwise, this method produces an enormously inflated 
estimate \cite{val-thesis}.

Recently, attempts have been made to provide better estimators. Valiant, 
provides a canonical estimation approach based on first estimating the unseen 
region of the support\cite{val-thesis}. This algorithm appears to perform 
very well in practice.  Batu provided an alternative approach, which bypasses 
estimating the probability mass functions, and relies on the more fundamental 
concept of \textit{collisions}\cite{batu2000testing,batu2013testing}, which 
has recently been simplified \cite{chan2014optimal}.

Both methods converge much more quickly than the naive approach. However, two 
basic limitations remain. First, these relatively recent approaches are not 
accompanied by any absolute guarantees of statistical confidence, so it is not 
clear how to build confidence intervals for a given estimate. Second, these 
cannot provide reliable estimates if none of the elements of the support 
recur in the samples (that is, when we never observe the same work-product 
twice in our sample sets).

It may seem unreasonable to hope to measure $\theta$ when our samples are so 
sparse in the space of work-products.  However, in machine learning,
classifiers can succeed in the face of this much sparsity, and we can use
this fact to estimate a lower bound on $\theta$ via \textbf{definition \ref{def:dist}}.

\paragraph{Experimental setup.}
We performed two experiments, soliciting respectively 900 and 2300 MTurk 
workers to
label images that depicting iconic cultural scenes, meals, ingredients, 
table-settings, and various utensils and cookware. In these experiments,
workers were randomly assigned to treatments, and depending on this 
assignment, were exposed to different framing primes, given a different 
set of initial images, and shown a different permutation of the test images. 
In all treatments (for both experiments), workers were 
given the same brief set of instructions before labeling any images.  The
framing prime, if one was shown, followed the instructions.  Workers then
labelled images, one at a time, providing five labels per image.  
For the purpose of analysis, we denote the first five images as the 
\textit{initial set}, and the last five as the \textit{test set}, but, 
cruicially, from
the perspective of the worker, no distinction was aparent.
In the second experiment, treatments which received framing primes were
not shown an initial set, so labeled only five images (the test set).
Table 1 sumarizes the various experimental treatments for both 
experiments.

\begin{table}[t]
\centering
	\begin{tabular}{ l  l  l }
		\hline                       
		Treatment & Framing prime & Initial image set	\\ 
		\hline                       
		$\textsc{ambg}$ & None & Ambiguous\\
		$\textsc{img:cult}$ & None & Cultural\\
		$\textsc{img:ingr}$ & None & Ingredients\\
		$\textsc{frm:cult}$ & Cultural & Cultural\\
		$\textsc{frm:ingr}$ & Cultural & Cultural\\
		\hline  
	\end{tabular}

	\caption{ \footnotesize{ 
		Workers were uniformly randomly assigned to one of the 
		treatments listed above. 
		The full funder names used were 
		``The Global Foundation for Cultural Recognition'' and 
		``The National Foundation for Nutritional Awareness''.  
		The ambiguous, cultural, and ingredients initial image sets are shown 
		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
	}}
	\label{table:1}
\end{table}

\begin{figure}
	\centering
	\includegraphics[scale=0.7]{figs/tasks.pdf}
	\caption{Examples of slides used for the image labeling tasks. A) instructions shown to all workers; B) a framing slide; C) a slide from the initial set for treatment IMG:FOOD; D) a slide from the initial set for treatment IMG:OBJ; E) a slide from the test set shown in all treatments. The full set of slides used for all treatments is presented in the supplementary material.}
	\label{fig:task}
\end{figure}

\paragraph{The strength of inter-task effects}
The purpose of the first experiment was to compare the relative strength
of inter-task and framing effects.  In this experiment, the treatment 
\textsc{ambg} served as a base-case.  The other treatments differed from
\textsc{ambg} either in terms of the initial image set, or by the addition of a
framing prime.

The test images in this experiment 1 consisted of meals having
a strong, specific cultural connection (Fig. \ref{fig:task} shows an example).
The \textsc{ambg} treatment had an initial set which also consisted of meals,
but without more muted cultural overtones.  The initial images for treatment 
\textsc{img:cult} featured iconic cultural scenes (devoid of food) while 
those for treatment \textsc{img:ingr} consisted of isolated ingredients.
Treatments \textsc{frm:cult} and \textsc{frm:ingr} had the same initail images
as \textsc{ambg}, but had respectively a framing prime indicating that the
tasks were funded by a foundation for ``cultural recognition'' and
``nutritional awareness''.

We tested for inter-task effects by evaluating the performance of a Naive 
Bayes classifier when distinguishing the work-products from 
\textsc{img:cult} and \textsc{img:ingr}, and, separately, when distinguishing
those from \textsc{frm:cult} and \textsc{frm:ingr},
using only the labels that workers from these treatments
attributed to the test set of images.

can perform better than the actual difference in priming, so the performance 
of Naive Bayes classifier provides a lower bound on priming difference. We 
used leave-one-out validation to estimate the classifier per- formance. We 
tested for framing effects in a similar way, by training a Naive Bayes 
classifier to classify work-products among \textsc{frm:food} and 
\textsc{frm:obj}.

@@

%The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
%Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
%\textit{initial set} of five images labeled by workers contained objects such 
%as utensils, kitchenware, and table-settings, but no food items. In the 
%\textsc{img:food}, the initial set contained centered close-ups of meals, 
%without
%any surrounding objects (except sometimes the dish supporting the food). No 
%interruption or distinction made between the initial and test sets from the 
%view of the workers. To study the positional dependance of inter-task effects,
%these treatments were subdivided, and workers were shown one of five 
%permutations. There are of course 5! = 120 permutations of five images, but 
%investigating all permutations was too expensive, and probably redundant, so 
%we chose 5 permutations that ensure each image occupies each position within 
%the test set. We discuss the benefits and drawbacks of this choice in the 
%supplementary material.
%
%Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
%framing slide, which bore a message reading: ``Funded by the laboratory for 
%the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
%After the framing slide, workers in these treatments proceeded directly to 
%the test set (and so labeled only 5 images).
\paragraph{Inter-task effects and the orientation of focus.}
Since the initial images were chosen to emphasize either food (ingredients 
set) or culture (cultural set), we looked for effects on the number of 
culture- and food-oriented labels that workers attributed to the test image 
set.
